Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-04 PaperVictor.tex
Llegué a mirror stacking

    es esquemática? ¿La necesitamos? Está tan chica que es ilegible}

@@

\notaL{Aquí voy.}

Due to the absorptive nature of Si in the UV and visible region, it is relatively
difficult to design porous silicon omnidirectional mirrors in that region.
However, in the IR region, it is relatively easy to obtain highly reflective
and even omnidirectional photonic structures over a wide range. Therefore,
the average reflectance was optimized using the function $f_{1}$ (Eq. (\ref{F1}))
in the region of 850 to 3000 nm. It was found that the best value for
$\alpha $ is 1.2 and the minimum thickness is 60.4 $\mu$m, distributed in
90 periods. The complete design of the structure (named as ST-B) is graphed in Fig.
\ref{Fig3}(a).
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F4OptimizedNIRPC.pdf}
\end{center}
\caption{(a) Distribution of $\protect\lambda _{j}$ in the $j$-th period
modulated by the optimization of the function $f_{1}$ for the design of the
multilayer structure of 90 periods. (b) Mapping of the average reflectance
of the structures designed with different values of the $\protect\alpha $
and $N_{p}$ parameters. The optimized parameters are $\protect\alpha =1.2$
and 90 periods. (c) Mapping the calculated reflectance of the designed
structure with the optimized values for non polarized light. (d) Comparison of
reflectance spectra calculated and measured at different angles of incidence. The
gray band indicates the region in which the reflectance is greater than 95$\%$. Inset
there is a photograph of the synthesized structure.}
\label{Fig3}
\end{figure}

In Fig \ref{Fig3}(b) the average reflectance of structures
designed with different values of $\alpha$ and $N_{p}$ is mapped. As in the
previous case, the optimized parameters are within the zone of maximum
average reflectance. The reflectance calculation shows that this structure
has a wide quasi-omnidirectional gap that goes from 850 to 3000 nm and from
0${{}^\circ}$ to 70${{}^\circ}$ of incidence; the corresponding contour plot is
shown in Fig. \ref{Fig3}(c) and its average reflectance between $850-3000$ nm is
greater than 95\%. The measured and calculated reflectance spectra have very
similar characteristics as shown in Fig \ref{Fig3}(d).  The synthesized PS
multilayered 1D photonic structure has a quasi omnidirectional (from 0${{}^\circ}$
to 60${{}^\circ}$) band gap of approximately 1800 nm. The difference
between the calculated and measured spectra at the longer wavelengths can be
attributed to a thickness gradient along the depth, which is more pronounced in
the lower layers due to the restricted diffusivity of the electrolyte
through the structure itself \cite{Negro2003,Vincent1993} and interface roughness.

>>>>

    es esquemática? ¿La necesitamos? Está tan chica que es
    ilegible}\notaL{¿Qué es eso de $\lambda+1$? Creo que está mal}

@@

Due to the disipative nature of Si in the UV and the visible region, it is relatively
difficult to design porous silicon omnidirectional mirrors in that region.
However, in the IR region, it is relatively easy to obtain highly reflective
and even omnidirectional photonic structures over a wide
range. \notaL{Está rara la lógica: ¿optimizamos en esa región porque
  es fácil o usamos $f_1$ porque optimizar es fácil? Quizás primero
  debamos decir que nos interesa esa región y que como es fácil,
  usamos $f_1$.}
Therefore,
the reflectance average in the region of 850 to 3000 nm and for all
angles was optimized using the function $f_{1}$ (Eq. (\ref{F1})), yielding
$\alpha=1.2$ with $N_p=90$ and a thickness of 60.4 $\mu$m. \notaL{Aquí
  me vuelve a confundir. ¿90 es el ancho óptimo o
  es el ancho mínimo que permitió... qué?} The resulting design
wavelengths of the structured, designated as ST-B, \notaL{¿Por qué se llaman así? ¿Qué significa
  ST?} are shown in Fig.
\ref{Fig3}(a).
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F4OptimizedNIRPC.pdf}
\end{center}
\caption{(a) Design wavelengths $\lambda_j$ as a function of period
  number $j$ for sample ST-B. (b) Average reflectance $\braket{R}$
for different values of the parameters $\alpha$
and $N_p$ parameters. \notaL{Cambia el letrero en la figura} The
optimized parameters $\protect\alpha =1.2$
and $N_p=90$ are displayed as a white spot.\notaL{No se ve que sea el
  óptimo. Quizás se necesiten línes de contorno más juntas.} (c)
Calculated reflectance of the optimized
structure for non polarized light.\notaL{¿QUé indica la raya punteada
  y el letrero en la figura?} (d) Comparison of
the calculated and measured spectra  for several angles of incidence. The
gray band indicates the region in which the reflectance is greater than 95$\%$. Inset:
photograph of the synthesized structure.}
\label{Fig3}
\end{figure}

\notaL{Tengo los mismos comentarios que para la figura previa.}
Fig \ref{Fig3}(b) shows $\braket{R}$ for
different values of $\alpha$ and $N_{p}$. As in the
previous case, the optimized parameters are within the zone of maximum
average reflectance. \notaL{No debería ser el mismísimo máximo y no
  nada más en la zona?} The reflectance calculation  is
shown in Fig. \ref{Fig3}(c).  This structure
has a wide quasi-omnidirectional gap with $R(\lambda,\theta)>0.95$
with $\lambda$ from 850 to 3000 nm and $\theta$ from
$0^\circ$ to $70^\circ$.\notaL{Me da la impresión que confundías
  promedio con reflectancia} The measured and calculated reflectance
are compared  for several angles in Fig \ref{Fig3}(d). The synthesized PS
multilayered 1D photonic structure behaves as a quasi omnidirectional
mirror for $0^\circ\le\theta\le 60^\circ$ with a bandwidth of approximately 1800 nm. The difference
between the calculated and measured spectra at the longer wavelengths can be
attributed to a thickness gradient along the depth,\notaL{No entiendo:
  está diseñada para tener un gradiente de ancho. Te refieres a un
  gradiente adicional al diseñado?} which is more pronounced in
the lower layers due to the restricted diffusivity of the electrolyte
through the structure itself \cite{Negro2003,Vincent1993} and
interface roughness \notaL{No se entiende si este es otro efecto o si
  la rugosidad produce un gradiente de anchos}.
